Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider

### 2019-10-21 main.tex
Updating higgsino limits and references

The optimal search strategy for finding electroweakinos is highly dependent on
their mass spectra \cite{Han:2013kza}. Phenomenological collider studies on
finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at a
100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
Berlin:2015aba, Cirelli:2014dsa}, which in turn draw inspiration from earlier
studies done for the LHC \cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
Schwaller:2013baa, Baer:2014cua, Han:2014kaa}.
For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino
LSPs using the monojet channel is about $1.4$~TeV.  The reach
can be increased to $\sim3$ TeV with a disappearing tracks search.
Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
with masses up to 1.5 TeV for an inter-state mass splitting of around 1 GeV  can be
discovered at a 100 TeV $pp$ collider with $\sim7\ \text{ab}^{-1}$
of data \cite{Bramante:2014tba}.

Well-separated spectra have been studied in \cite{Gori:2014oua,
Acharya:2014pua} using multi-lepton channels, of the form

>>>>

The optimal search strategy for finding electroweakinos is highly dependent on
their mass spectra \cite{Han:2013kza}. Phenomenological collider studies on
finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at a
100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
  Berlin:2015aba, Cirelli:2014dsa, Mahbubani:2017gjh, Mahbubani:2018tin,
Fukuda:2017jmk, Saito:2019rtg},
  \ap{which in turn draw inspiration from earlier
studies done for the LHC \cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
Schwaller:2013baa, Baer:2014cua, Han:2014kaa}}.
For $3\ \text{ab}^{-1}$ of data, the \ap{strongest projected discovery reaches for pure Wino
(Higgsino) LSPs using the monojet channel with disappearing tracks at a 100 TeV
collider is about $4.8$~TeV (1.1~TeV) \cite{Saito:2019rtg}}\st{. The reach
can be increased to $\sim3$ TeV (870 GeV) with disappearing tracks
searches.}\Adarsh{Shufang, does this look ok to you? Why are the results in
\cite{Saito:2019rtg} so much better than those in \cite{Low:2014cba}?} 
For mass splittings of about 20-30 GeV, neutralinos up to 1 TeV can be excluded 
using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
with masses up to 1.5 TeV for an inter-state mass splitting of around 1 GeV  can be
discovered at a 100 TeV $pp$ collider with $\sim7\ \text{ab}^{-1}$
of data \cite{Bramante:2014tba}.

Well-separated spectra have been studied using multi-lepton channels
\cite{Gori:2014oua, Acharya:2014pua}, of the form
